
---
title: "Interesting Forecast Applications with R"
author: "Yusuf Hancer - IE360 - Spring 2020"
---


```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("D:/GitKraken/spring20-yhancer/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("D:/GitKraken/spring20-yhancer/example_homework_0.Rmd",output_format="html_document")
```

1. [Autocorrelation and Time Series Methods](https://online.stat.psu.edu/stat462/node/188/)

    This is an example of autoregressive models which is when a value from a time series is regressed on previous values from the same time series. In example 2, it can be observed that in the annual number of worldwide earthquakes with magnitude greater than 7 on the Richter scale, the lag-3 can be used as predictor.
    
2. [The Bias-Variance Tradeoff](https://towardsdatascience.com/understanding-the-bias-variance-tradeoff-165e6942b229)
  
    The motivation for creating a model is to predict the future with small errors. Upon preparing the model, creators are tend to make the model too complex so that the model pays too much attention to the training set which results in learning the noise however the reverse is also wrong as the model is too simple than it cannot predict the future at all. The modeler must find an optimal balance of bias and variance in order to fit the model.
    